Highlighting Disputed Information on the Web

### 2009-05-20 papers/uist_thinklink/uist_rebuttal.txt

The users were primarily concerned with two issues: (i) a perceived lack of novelty (primarily reviewer 1), (ii) worries about bootstrapping

= Novelty =

While web annotation systems are old hat, as reviewer 1 stated: "[Think Link] appears to be the first work to make use of Open Hypermedia for identifying disputed statements on the web"

You could of course use an existing, less structured, annotation system to mark disputed information: either insert a comment saying that you disagree with something, or insert a link to conflicting information.

The key contribution of Think Link is that, by imposing additional structure on annotations, it provides a better experience for finding and marking disputed information. In particular:

* Since Think Link knows when snippets are making the same claim, a user can ask to not be notified about a particular claim again - seeing many annotations about the same claims would be annoying.

* Since Think Link links to an argumentation graph rather than an arbitrary web page, a link will always give a user whatever the community believes to be the best evidence for or against a claim, rather than what a particular user liked.

* Think Link reduces "noise" by not allowing users to add arbitrary text to a page, only allowing a user to link to a structured claim node, and using voting to determine what claims and snippets are actually worth showing to users.

* Think Link makes it easy for a user to mark many snippets that make the same same claim "in bulk" and suggests claims and topics.

= Bootstrapping =

Bootstrapping is an important challenge for a tool such as Think Link and something we could discuss in more depth.

Our set of claims has been bootstrapped by important lists of disputed claims from several existing web sites. Currently we have Snopes and a couple of debate-focussed websites. We also have a task on Amazon Mechanical Turk to tell us more disputed claims.

Our set of snippets has been bootstrapped by using a task on Amazon Mechanical Turk. Turk users are presented with a list of candidate snippets for a claim and asked to tell us which snippets are indeed making the claim. The candidate snippets come from a Yahoo BOSS search. We have found that users will mark up 10 snippets for only 2 cents - allowing us to build data sat very quickly provided

Our connections between claims are currently entered entirely manually, but in future we plan to bootstrap that using mechanical turk too.

Reviewer 5 was concerned that, since a web page saying global warming did not exist was less popular, it would be less likely to be marked than one that said it did exist. In fact the converse is true. Since there are more activists who believe that global warming exists, more people will use search engines to find and highlight pages that say global warming does not exist, and thus such pages are more likely to be highlighted.

### 2009-10-10 papers/www_disputefinder/disputefinder.tex
Started writing paper

%\documentclass{article}
\documentclass{chi2009}
\usepackage{times}
%\usepackage{uist}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}

@@

% --- Copyright notice ---
\conferenceinfo{UIST'09}{October 4-7, 2009, Victoria, BC, Canada}
\CopyrightYear{2009}
\crdata{x-xxxxx-xxx-x/xx/xxxx}

% Uncomment the following line to hide the copyright notice
\toappear{}
% ------------------------

@@

\title{Exposing and Exploring Disputed Statements on the Web}

@@

\author{
\parbox[t]{9cm}{\centering
	     {\em Author names removed for blind review}\\
}
}

@@

%RULE: Don't cite media reports unless I have to

\abstract
Think Link is a tool that helps users know when information they read on the web is disputed. 
As a user browses the web, Think Link highlights snippets of text that make claims that users have identified as contentious. 
If a user clicks on a highlighted snippet, Think Link displays an argument graph showing the best evidence for and against the claim the snippet is making.

Users provide all of Think Link's information: they create new claims, mark new snippets, connect snippets to claims, and vote for the best evidence.
Think Link is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension to see when statements they read are disputed and find other sources that present alternative viewpoints.

\classification{H5.2 [Information interfaces and presentation]:
User Interfaces. - Graphical user interfaces.}

@@

In this paper we present Think Link, a tool that helps users discover when information they read is disputed, and helps users find sources with alternative points of view. 
If a user has installed the Think Link browser extension then it will highlight snippets of text on the web that make disputed claims (Figure~\ref{highlight}). 
When a user clicks on a highlighted snippet, Think Link presents an argument graph that shows the best evidence for and against the claim (Figure~\ref{claimview}).

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/v2_highlight_shadow.png}
	\caption{Think Link highlights snippets that make disputed claims}
	\label{highlight}
	\end{center}
\end{figure}

@@

Think Link relies on users to identify disputed claims, to find instances of these claims on web pages, and to vote for the sources that provide the best support or opposition for a claim. 
Think Link is designed to cater to two primary usage scenarios:

\begin{description}
\item[Activists] care strongly about particular issues. They use Think Link to mark snippets that make claims that they disagree with. They are motivated by a desire to make other readers see that these claims are disputed and learn about the opposing point of view.

\item[Sceptical Readers] want to know when information they read is disputed so that they can avoid being misled. They install Think Link as a browser extension so that it will highlight disputed claims and show them opposing points of view.
\end{description}

@@

Think Link's design was guided by two user studies in which we observed users' behavior as they performed tasks fitting the usage scenarios for Activist and Sceptical Reader.

@@

% \begin{figure}[tb]
% 	\begin{center}
% 	\includegraphics[width=7.7cm]{../screenshots/summary_graph.png}
% 	\caption{Think link connects claims to each other and to web snippets}
% 	\label{summarygraph}
% 	\end{center}
% \end{figure}

@@

Think Link builds on prior work in several different areas. The argument graph is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}. 
The idea of highlighting potentially untrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}. Tagging Systems~\cite{Marlow2006} influenced the way Think Link uses the community to collect and filter information. Think Link's snippets are influenced by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.

What makes Think Link interesting is the way that it applies ideas from these different domains to the task of helping users deal with misinformation and bias on the web.

@@

Think Link's argument graph is inspired by IBIS\footnote{Issue Based Information System}~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}. IBIS tools model debate as a graph of issues, positions, and arguments. While the graph structure varies between tools, most tools allow a node to support or oppose another node and allow a node to be linked to an issue.

Cohere~\cite{Shum2008} allows a user to specify one or more related URLs when creating a new claim, and provides a Firefox extension to help a user create a claim about a web page they are reading. Unlike Think Link, Cohere is not designed to be used to alert users about disputed snippets. Cohere works with URLs rather than snippets and does not allow one to connect a new URL to an existing claim created by someone else.

Although Think Link's argument graph is similar to that used by IBIS tools, it is used for a different purpose. 
In Think Link the focus is on snippets; the argument graph is used to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular claim. 
A user is expected to create a new claim only when they want to group together several snippets that make that claim. 
A Think Link user is expected to form an opinion primarily by looking at the snippets and the pages in which they appear, rather than by looking at the argument graph itself. By contrast, in an IBIS tool such as gIBIS~\cite{Conklin1987a}, the focus is on the argument graph. A gIBIS user is encouraged to break their argument down into as many separate ideas as possible and is expected to use the graph itself to reach a conclusion. In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims but is associated with many snippets.

Isenmann and Reuter~\cite{Isenmann1997} identified a number of problems with using IBIS tools to help people resolve disputes and make decisions. Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their disputes, and that users found it difficult to properly encode a complex issue as an argument graph. We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and conflict resolution, they are less of a problem for a tool like Think Link that is designed for identifying snippets that represent conflicting points of view.

Think Link uses a simple IBIS-like graph structure in which claims support, oppose, or relate-to other claims. Several alternative graph structures have been proposed for describing arguments and design rationale. WinWin~\cite{Boehm2006} models the different stakeholders and their different motives. The Toulmin Model~\cite{toulmin1958} breaks down the logical way in which arguments are formed from evidence, rules, and exceptions. QOS~\cite{Maclean1991} explicitly states the criteria used to choose between positions. More formal models such as Carneades~\cite{Gordon2007} have been used for artificial intelligence.

@@

If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}. Snopes is a database of urban legends that the site owners investigated to determine whether they are true. 
Think Link's database automatically imports all contentious claims identified by Snopes.
FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts. The advantage of Think Link is that it tells you when information on web sites is disputed automatically, without requiring you to suspect that information might be disputed and look for it on another site.

@@

% FactCheck updates infrequently enough that we have been able to manually add its disputed claims to Think Link as they appear.

@@

NewsCube~\cite{Park2009} and MediaCloud\footnote{http://mediacloud.org} use statistics to help readers avoid media bias. NewsCube finds articles on the same topic that have different biases. MediaCloud shows which different words different news sources associate with the same topic. Unlike Think Link, these tools find contrasting pages about broad topics, rather than trying to find particular claims that are disputed or snippets that make disputed claims.

Several authors have created tools that help users know when to trust information on Wikipedia\footnote{http://wikipedia.org}. WikiTrust~\cite{Adler2008a} highlights passages on wikipedia that have been written recently or written by untrusted editors. Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is. Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest. Unlike these Wikipedia-based systems, Think Link does not use edit history to determine when text is untrustworthy; rather it relies on a community of activist users.

@@

Think Link is an example of an Open Hypermedia system~\cite{Bouvin2000}. Like other Open Hypermedia systems, Think Link allows users to lay an additional link structure over an existing hypertext document. Think Link differs from prior open hypermedia systems in its focus on revealing contentious arguments. While other systems such as HyperDISCO~\cite{Wiil1996} could be used to link a snippet to a contentious claim, they do not provide user interface support to make this easy.

@@

Tagging Systems~\cite{Marlow2006,Golder2006} allow users to collect and organize information by associating it with an ad-hoc collection of tags. Notable tagging systems include del.icio.us\footnote{http://del.icio.us} which uses tags to organize web pages, and Flickr\footnote{http://flickr.com} which associates tags with photos. While Think Link also allows users to organize information from other sources, it does not use tags.

@@

SpinSpotter\footnote{http://spinspotter.com} allows a user to mark snippets that contain spin or bias. A user can comment on why a snippet is biased and rewrite the snippet in a neutral way. While SpinSpotter and Think Link both draw attention to biased or inaccurate snippets, they do different things with the snippets. SpinSpotter lets users annotate a snippet with comments specific to that particular snippet, while Think Link treats a snippet as being an instance of a shared claim, and links all snippets identified as making that claim to a shared node in the argument graph that is linked to other points of view.

@@

ClaimSpotter~\cite{Sereno2005,Sereno2004} allows one to mark up a scholarly paper with logical subject-verb-object triples describing important claims made in the document. Entity Workspace~\cite{Bier2006} does something similar for intelligence documents. Like Think Link, these tools allow a user to mark the claims being made in a document, however these tools are more formal and are designed to extract knowledge rather than informally mark disputed snippets.

@@

Several tools layer an alternative navigation graph over information on the web. TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages. ScentHighlights~\cite{Chi2005a} highlights snippets of text that relate to topics the user has expressed interest in. Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books. Think Link also creates new links between information, but it's links are created by users, rather than being mined automatically.

@@

\section{The Think Link System}

For Sceptical Readers, Think Link highlights disputed snippets and links them to snippets on other web sites that present alternative points of view. For Activists, Think Link makes it easy for users to mark snippets about issues they care about and connect them into an argument graph.

@@

If a sceptical reader has installed the Think Link browser extension, Think Link will draw attention to snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}). If a user hovers their mouse over a highlighted snippet then Think Link displays a tooltip giving the disputed claim. Clicking on a highlighted snippet reveals a visualization showing the best evidence for and against the claim, as determined by the user community (Figure~\ref{claimview}).

@@

Since the purpose of a highlight is to alert the user to claims that they had not realized were contentious, there is little benefit in highlighting snippets that make claims that the user already realizes are contentious. A user can click the ``don't highlight this claim again'' button to tell Think Link that they are aware of the contentious nature of this claim and do not wish to be alerted about it again.

Normally Think Link will only highlight snippets that make disputed claims that the user has not asked to ignore, and snippets marked by the user themselves. If the user wants to see all snippets on a page then they can do so by opening the Think Link sidebar.

@@

Once a sceptical reader has identified a claim that they are interested in, they can use Think Link's claim browser interface (Figure~\ref{panels}) to investigate the evidence for and against it, and to see what other contentious claims have been made about related issues.

@@

To preserve visual consistency, Think Link uses the same claim browser interface for the small popup interface as for the full-window interface. When used as a popup browser, the interface shows only one panel. Clicking on an item in the panel scrolls the display to the right to reveal a new panel. If the user clicks the ``back'' button, the interface will quickly scroll left back to the previous panel.

@@

Think Link's claim graph is a variant of the IBIS~\cite{Rittel1973} model. There are three types of nodes: snippets, claims, and topics. 
A snippet is a region of text taken from a web page; a claim is a statement about the world or a position that one can take on some issue; and a topic is an issue that a claim might address or a thing that a claim might be about. Nodes are connected together by typed, directed, links. 
There are three link types: supports, opposes, and relates-to. A snippet or claim can support, oppose, or relate-to a claim; and any node can relate-to a topic.

Think Link uses the list of page titles on Wikipedia as a seed-set for its topics. This allows Think Link to use the Wikify~\cite{Mihalcea2007} algorithm to automatically suggest topics for snippets and provides us with a comprehensive ready-made set of topics with well-maintained descriptions and synonyms.

Think Link's graph model is simpler than that used by gIBIS~\cite{Conklin1987a}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, and we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to link type. 
While Think Link's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, we have found that it is sufficient for the conflict discovery and snippet organization task that Think Link is designed for. 
We have also found that the smaller set of less precise link and node types reduces the mental effort required to create an argument graph.

@@

One danger in a voting system is that a large group of people may drown out the opinions of their opponents by voting down their opinions. Think Link uses two strategies to try to reduce this problem. Firstly, positive votes count for more than negative votes. Thus if two different groups are voting up their own evidence and voting down the opposing group's evidence, it is still likely that the opinions of both groups will be relatively prominent. Secondly, a piece of evidence only competes against other pieces of evidence on the same side of the argument, thus even if supporters of one side are voting up their own evidence, this will not push down evidence on the other side -- though of course they may vote up bad arguments for the opposing point of view. We anticipate that we will eventually need to introduce a moderation system similar to that used in Wikipedia, allowing trusted users to override popular opinion when things go wrong. 
\todo{Talk about whether we know if this works}

@@

If an Activist has installed the Think Link browser extension then they can create a snippet by selecting text on a web page and selecting either ``This is disputed'' or ``This is interesting'' from the context menu (Figure~\ref{createprocess}). A user selects ``This is disputed'' if they believe that readers of that snippet should be alerted that the snippet is making a claim that is disputed. A user selects ``This is interesting'' if they believe that the snippet contains useful evidence that could be useful for readers investigating a disputed claim.

The only difference between selecting ``this is disputed'' and ``this is interesting'' is that Think Link remembers which you used when you marked a snippet. A snippet is only highlighted in red for other users if it is connected to a disputed claim. The main reason for having two different options is to show users what kinds of information Think Link expects them to mark as snippets.
\todo{Say something smart about the difference}

@@

Think Link does not require a user to specify the claim a snippet is making at the point at which they mark it. Instead, Think Link encourages a user to gather many snippets and then use the claim browser interface to associate claims with snippets in bulk.
One anticipated usage scenario for Think Link is an activist user who uses a search engine to find a large number of snippets that make a claim that they disagree with. 
In this case, the user can save time by first collecting all their snippets, and then attaching all the snippets to their disputed claim at the same time.

Think Link provides three ways for a user to associate a claim with a snippet:

\begin{description}
\item[Claim first:] If a user navigates to a claim and clicks the ``add snippet'' button, Think Link will suggest unattached snippets that the user created recently and that are textually similar to the wording of the claim or other snippets currently attached to the claim (Figure~\ref{snipclaim}). A user can attach a suggested snippet to the claim by clicking on icons representing ``supports'', ``opposes'', or ``relates-to'' link types. If Think Link does not suggest the right snippets then Think Link can guide the suggestions by entering keywords into the text box above the suggestion list.

@@

\item[Snippet first:] If a user selects the ``unfiled'' tab at the top of the claim browser then Think Link will show a list of all the snippets that they have marked but not yet associated with a claim or a topic (Figure~\ref{sniptopic}). If the user selects an unfiled snippet then Think Link will suggest claims or topics that the user might want to associate with that snippet. As with the claim-first method, a user can guide the suggestions by entering keywords. If the correct claim is not suggested then the user can create a new claim by typing it into the text box and clicking the ``add'' button.

@@

\item[Immediate:] A user can select a claim for a snippet that they have just marked. When a user marks a snippet, Think Link will initially highlight it in blue to show that the snippet is not currently associated with a claim or topic and will not be shown to other users. If the user clicks on the highlighted snippet, then Think Link will bring up the same suggestion panel used in the ``snippet first'' method.
\end{description}

Think Link uses the same suggestion system to suggest connections between claims. It is important to make sure that the argument graph stays well connected as it grows. If users create duplicate claims or don't connect their claims to existing claims then the graph becomes less useful. Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to create a suggested connection with a single click.

>>>>

%\documentclass{article}
\documentclass{www2010-submission}
\usepackage{times}
%\usepackage{uist}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}

@@

\toappear

@@

\title{Highlighting Disputed Information on the Web}

@@

\numberofauthors{5}

\author{
\alignauthor Rob Ennals\\
       \affaddr{Intel Labs Berkeley}\\
       \affaddr{2150 Shattuck Ave}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{robert.ennals@intel.com}
\alignauthor Beth Trushkowsky\\
       \affaddr{Computer Science Division}\\
       \affaddr{University of California at Berkeley}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{trush@berkeley.edu}
\alignauthor John Mark Agosta\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
}

\additionalauthors{+ Whoever else wants to join in}

@@

%RULE: Don't cite media reports unless I have to - some reviewers don't like it

\abstract
Dispute Finder is a tool that helps users know when information they read on the web is disputed. 
As a user browses the web, Dispute Finder highlights snippets of text that make claims that users have identified as contentious. 
If a user clicks on a highlighted snippet, Dispute Finder displays an argument graph showing the best evidence for and against the claim the snippet is making.

Users provide all of Dispute Finder's information: they create new claims, mark new snippets, connect snippets to claims, and vote for the best evidence.
Dispute Finder is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Dispute Finder with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Dispute Finder as a browser extension to see when statements they read are disputed and find other sources that present alternative viewpoints.

\category{H.4.m}{Information Systems}{Miscellaneous}
\category{H.4.2}{Information Systems}{Decision Support}
\category{H.5.2}{User Interfaces}{Graphical User Interfaces}

@@

In this paper we present Dispute Finder, a tool that helps users discover when information they read is disputed, and helps users find sources with alternative points of view. 
If a user has installed the Dispute Finder browser extension then it will highlight snippets of text on the web that make disputed claims (Figure~\ref{highlight}). 
When a user clicks on a highlighted snippet, Dispute Finder presents an argument graph that shows the best evidence for and against the claim (Figure~\ref{claimview}).

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/v2_highlight_shadow.png}
	\caption{Dispute Finder highlights snippets that make disputed claims}
	\label{highlight}
	\end{center}
\end{figure}

@@

Dispute Finder relies on users to identify disputed claims, to find instances of these claims on web pages, and to vote for the sources that provide the best support or opposition for a claim. 
Dispute Finder is designed to cater to two primary usage scenarios:

\begin{description}
\item[Activists] care strongly about particular issues. They use Dispute Finder to mark snippets that make claims that they disagree with. They are motivated by a desire to make other readers see that these claims are disputed and learn about the opposing point of view.

\item[Sceptical Readers] want to know when information they read is disputed so that they can avoid being misled. They install Dispute Finder as a browser extension so that it will highlight disputed claims and show them opposing points of view.
\end{description}

@@

Dispute Finder's design was guided by two user studies in which we observed users' behavior as they performed tasks fitting the usage scenarios for Activist and Sceptical Reader.

@@

% \begin{figure}[tb]
% 	\begin{center}
% 	\includegraphics[width=7.7cm]{../screenshots/summary_graph.png}
% 	\caption{Dispute Finder connects claims to each other and to web snippets}
% 	\label{summarygraph}
% 	\end{center}
% \end{figure}

@@

Dispute Finder builds on prior work in several different areas. The argument graph is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}. 
The idea of highlighting potentially untrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}. Tagging Systems~\cite{Marlow2006} influenced the way Dispute Finder uses the community to collect and filter information. Dispute Finder's snippets are influenced by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.

What makes Dispute Finder interesting is the way that it applies ideas from these different domains to the task of helping users deal with misinformation and bias on the web.

@@

Dispute Finder's argument graph is inspired by IBIS\footnote{Issue Based Information System}~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}. IBIS tools model debate as a graph of issues, positions, and arguments. While the graph structure varies between tools, most tools allow a node to support or oppose another node and allow a node to be linked to an issue.

Cohere~\cite{Shum2008} allows a user to specify one or more related URLs when creating a new claim, and provides a Firefox extension to help a user create a claim about a web page they are reading. Unlike Dispute Finder, Cohere is not designed to be used to alert users about disputed snippets. Cohere works with URLs rather than snippets and does not allow one to connect a new URL to an existing claim created by someone else.

Although Dispute Finder's argument graph is similar to that used by IBIS tools, it is used for a different purpose. 
In Dispute Finder the focus is on snippets; the argument graph is used to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular claim. 
A user is expected to create a new claim only when they want to group together several snippets that make that claim. 
A Dispute Finder user is expected to form an opinion primarily by looking at the snippets and the pages in which they appear, rather than by looking at the argument graph itself. By contrast, in an IBIS tool such as gIBIS~\cite{Conklin1987a}, the focus is on the argument graph. A gIBIS user is encouraged to break their argument down into as many separate ideas as possible and is expected to use the graph itself to reach a conclusion. In Dispute Finder it is perfectly acceptable to have a claim that is not linked to any other claims but is associated with many snippets.

Isenmann and Reuter~\cite{Isenmann1997} identified a number of problems with using IBIS tools to help people resolve disputes and make decisions. Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their disputes, and that users found it difficult to properly encode a complex issue as an argument graph. We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and conflict resolution, they are less of a problem for a tool like Dispute Finder that is designed for identifying snippets that represent conflicting points of view.

Dispute Finder uses a simple IBIS-like graph structure in which claims support, oppose, or relate-to other claims. Several alternative graph structures have been proposed for describing arguments and design rationale. WinWin~\cite{Boehm2006} models the different stakeholders and their different motives. The Toulmin Model~\cite{toulmin1958} breaks down the logical way in which arguments are formed from evidence, rules, and exceptions. QOS~\cite{Maclean1991} explicitly states the criteria used to choose between positions. More formal models such as Carneades~\cite{Gordon2007} have been used for artificial intelligence.

@@

If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}. Snopes is a database of urban legends that the site owners investigated to determine whether they are true. 
Dispute Finder's database automatically imports all contentious claims identified by Snopes.
FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts. The advantage of Dispute Finder is that it tells you when information on web sites is disputed automatically, without requiring you to suspect that information might be disputed and look for it on another site.

@@

% FactCheck updates infrequently enough that we have been able to manually add its disputed claims to Dispute Finder as they appear.

@@

NewsCube~\cite{Park2009} and MediaCloud\footnote{http://mediacloud.org} use statistics to help readers avoid media bias. NewsCube finds articles on the same topic that have different biases. MediaCloud shows which different words different news sources associate with the same topic. Unlike Dispute Finder, these tools find contrasting pages about broad topics, rather than trying to find particular claims that are disputed or snippets that make disputed claims.

Several authors have created tools that help users know when to trust information on Wikipedia\footnote{http://wikipedia.org}. WikiTrust~\cite{Adler2008a} highlights passages on wikipedia that have been written recently or written by untrusted editors. Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is. Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest. Unlike these Wikipedia-based systems, Dispute Finder does not use edit history to determine when text is untrustworthy; rather it relies on a community of activist users.

@@

Dispute Finder is an example of an Open Hypermedia system~\cite{Bouvin2000}. Like other Open Hypermedia systems, Dispute Finder allows users to lay an additional link structure over an existing hypertext document. Dispute Finder differs from prior open hypermedia systems in its focus on revealing contentious arguments. While other systems such as HyperDISCO~\cite{Wiil1996} could be used to link a snippet to a contentious claim, they do not provide user interface support to make this easy.

@@

Tagging Systems~\cite{Marlow2006,Golder2006} allow users to collect and organize information by associating it with an ad-hoc collection of tags. Notable tagging systems include del.icio.us\footnote{http://del.icio.us} which uses tags to organize web pages, and Flickr\footnote{http://flickr.com} which associates tags with photos. While Dispute Finder also allows users to organize information from other sources, it does not use tags.

@@

SpinSpotter\footnote{http://spinspotter.com} allows a user to mark snippets that contain spin or bias. A user can comment on why a snippet is biased and rewrite the snippet in a neutral way. While SpinSpotter and Dispute Finder both draw attention to biased or inaccurate snippets, they do different things with the snippets. SpinSpotter lets users annotate a snippet with comments specific to that particular snippet, while Dispute Finder treats a snippet as being an instance of a shared claim, and links all snippets identified as making that claim to a shared node in the argument graph that is linked to other points of view.

@@

ClaimSpotter~\cite{Sereno2005,Sereno2004} allows one to mark up a scholarly paper with logical subject-verb-object triples describing important claims made in the document. Entity Workspace~\cite{Bier2006} does something similar for intelligence documents. Like Dispute Finder, these tools allow a user to mark the claims being made in a document, however these tools are more formal and are designed to extract knowledge rather than informally mark disputed snippets.

@@

Several tools layer an alternative navigation graph over information on the web. TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages. ScentHighlights~\cite{Chi2005a} highlights snippets of text that relate to topics the user has expressed interest in. Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books. Dispute Finder also creates new links between information, but it's links are created by users, rather than being mined automatically.

@@

\section{The Dispute Finder System}

For Sceptical Readers, Dispute Finder highlights disputed snippets and links them to snippets on other web sites that present alternative points of view. For Activists, Dispute Finder makes it easy for users to mark snippets about issues they care about and connect them into an argument graph.

@@

If a sceptical reader has installed the Dispute Finder browser extension, Dispute Finder will draw attention to snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}). If a user hovers their mouse over a highlighted snippet then Dispute Finder displays a tooltip giving the disputed claim. Clicking on a highlighted snippet reveals a visualization showing the best evidence for and against the claim, as determined by the user community (Figure~\ref{claimview}).

@@

Since the purpose of a highlight is to alert the user to claims that they had not realized were contentious, there is little benefit in highlighting snippets that make claims that the user already realizes are contentious. A user can click the ``don't highlight this claim again'' button to tell Dispute Finder that they are aware of the contentious nature of this claim and do not wish to be alerted about it again.

Normally Dispute Finder will only highlight snippets that make disputed claims that the user has not asked to ignore, and snippets marked by the user themselves. If the user wants to see all snippets on a page then they can do so by opening the Dispute Finder sidebar.

@@

Once a sceptical reader has identified a claim that they are interested in, they can use Dispute Finder's claim browser interface (Figure~\ref{panels}) to investigate the evidence for and against it, and to see what other contentious claims have been made about related issues.

@@

To preserve visual consistency, Dispute Finder uses the same claim browser interface for the small popup interface as for the full-window interface. When used as a popup browser, the interface shows only one panel. Clicking on an item in the panel scrolls the display to the right to reveal a new panel. If the user clicks the ``back'' button, the interface will quickly scroll left back to the previous panel.

@@

Dispute Finder's claim graph is a variant of the IBIS~\cite{Rittel1973} model. There are three types of nodes: snippets, claims, and topics. 
A snippet is a region of text taken from a web page; a claim is a statement about the world or a position that one can take on some issue; and a topic is an issue that a claim might address or a thing that a claim might be about. Nodes are connected together by typed, directed, links. 
There are three link types: supports, opposes, and relates-to. A snippet or claim can support, oppose, or relate-to a claim; and any node can relate-to a topic.

Dispute Finder uses the list of page titles on Wikipedia as a seed-set for its topics. This allows Dispute Finder to use the Wikify~\cite{Mihalcea2007} algorithm to automatically suggest topics for snippets and provides us with a comprehensive ready-made set of topics with well-maintained descriptions and synonyms.

Dispute Finder's graph model is simpler than that used by gIBIS~\cite{Conklin1987a}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, and we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to link type. 
While Dispute Finder's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, we have found that it is sufficient for the conflict discovery and snippet organization task that Dispute Finder is designed for. 
We have also found that the smaller set of less precise link and node types reduces the mental effort required to create an argument graph.

@@

One danger in a voting system is that a large group of people may drown out the opinions of their opponents by voting down their opinions. Dispute Finder uses two strategies to try to reduce this problem. Firstly, positive votes count for more than negative votes. Thus if two different groups are voting up their own evidence and voting down the opposing group's evidence, it is still likely that the opinions of both groups will be relatively prominent. Secondly, a piece of evidence only competes against other pieces of evidence on the same side of the argument, thus even if supporters of one side are voting up their own evidence, this will not push down evidence on the other side -- though of course they may vote up bad arguments for the opposing point of view. We anticipate that we will eventually need to introduce a moderation system similar to that used in Wikipedia, allowing trusted users to override popular opinion when things go wrong. 
\todo{Talk about whether we know if this works}

@@

If an Activist has installed the Dispute Finder browser extension then they can create a snippet by selecting text on a web page and selecting either ``This is disputed'' or ``This is interesting'' from the context menu (Figure~\ref{createprocess}). A user selects ``This is disputed'' if they believe that readers of that snippet should be alerted that the snippet is making a claim that is disputed. A user selects ``This is interesting'' if they believe that the snippet contains useful evidence that could be useful for readers investigating a disputed claim.

The only difference between selecting ``this is disputed'' and ``this is interesting'' is that Dispute Finder remembers which you used when you marked a snippet. A snippet is only highlighted in red for other users if it is connected to a disputed claim. The main reason for having two different options is to show users what kinds of information Dispute Finder expects them to mark as snippets.
\todo{Say something smart about the difference}

@@

Dispute Finder does not require a user to specify the claim a snippet is making at the point at which they mark it. Instead, Dispute Finder encourages a user to gather many snippets and then use the claim browser interface to associate claims with snippets in bulk.
One anticipated usage scenario for Dispute Finder is an activist user who uses a search engine to find a large number of snippets that make a claim that they disagree with. 
In this case, the user can save time by first collecting all their snippets, and then attaching all the snippets to their disputed claim at the same time.

Dispute Finder provides three ways for a user to associate a claim with a snippet:

\begin{description}
\item[Claim first:] If a user navigates to a claim and clicks the ``add snippet'' button, Dispute Finder will suggest unattached snippets that the user created recently and that are textually similar to the wording of the claim or other snippets currently attached to the claim (Figure~\ref{snipclaim}). A user can attach a suggested snippet to the claim by clicking on icons representing ``supports'', ``opposes'', or ``relates-to'' link types. If Dispute Finder does not suggest the right snippets then Dispute Finder can guide the suggestions by entering keywords into the text box above the suggestion list.

@@

\item[Snippet first:] If a user selects the ``unfiled'' tab at the top of the claim browser then Dispute Finder will show a list of all the snippets that they have marked but not yet associated with a claim or a topic (Figure~\ref{sniptopic}). If the user selects an unfiled snippet then Dispute Finder will suggest claims or topics that the user might want to associate with that snippet. As with the claim-first method, a user can guide the suggestions by entering keywords. If the correct claim is not suggested then the user can create a new claim by typing it into the text box and clicking the ``add'' button.

@@

\item[Immediate:] A user can select a claim for a snippet that they have just marked. When a user marks a snippet, Dispute Finder will initially highlight it in blue to show that the snippet is not currently associated with a claim or topic and will not be shown to other users. If the user clicks on the highlighted snippet, then Dispute Finder will bring up the same suggestion panel used in the ``snippet first'' method.
\end{description}

Dispute Finder uses the same suggestion system to suggest connections between claims. It is important to make sure that the argument graph stays well connected as it grows. If users create duplicate claims or don't connect their claims to existing claims then the graph becomes less useful. Dispute Finder tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to create a suggested connection with a single click.
